---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE, fig.width = 7, fig.height = 4)
library(tidyverse)
```

```{css}
body {
  font-family: Arial;
}

p {
  text-align: justify;
}

strong {
  color: #101010;
}
```

## What's happening in my emails?


```{r}
url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vRJTfkbSDaOgzplSQulCkgc1H5xJ2n5VnVDk1qzgsiYQRoJr0NHKQ2B5JX77orBEXK3J0wImxTUfRSf/pub?gid=916532695&single=true&output=csv"
logged_data <- read_csv(url)
latest_data <- logged_data %>%
  rename(timestamp = 1,
         category = 2,
         email_read = 3,
         email_reply = 4,
         time_to_view = 5,
         deleted = 6,
         inbox_size = 7) %>%
  mutate(category = str_replace(category, "\\(eg. Password Reset, Email Confirmation, Two Factor Authentication \\)", ""))
```

Throughout each and every day, I receive a flurry of notifications on my phone from my Gmail app. I have received yet another email. This constant flow of attention grabbing notifications has led to me zoning out every time I receive an email. Usually, I navigate to a point where I am able to delete this email before I have even truly considered what this email contained and why I was being sent it. As a result, I am investigating my email inbox, the emails I receive, and what I do with these. I created a simple Google form, where I can enter some brief information about an email, and how I behaved upon receiving it. Whenever I finished an email-receiving routine, I filled in this form with the corresponding information. 

There are several key ideas that I wanted to investigate:

### Email Types

```{r}
# summary values for email types
num_categories <- latest_data %>%
  distinct(category) %>%
  nrow()
```

*Question*: What category of email would you say best fits this email?

This question was of multiple choice form with 6 given options, but also included a 7th other option where the user can give an unspecified category if the email is not one of the 6 given. Given answers cover **`r num_categories` different categories**. These you will see displayed below:

```{r}
ggplot(data = latest_data) + 
  geom_bar(aes(x = category)) +
  labs(title = "Categories of Emails",
       x = "Categories",
       y = "Number of Emails")
```

### Behaviour as an Email is received

```{r}
# behaviour summary values
number_of_emails <- latest_data %>% 
  select(email_read) %>% 
  summarise(number_emails = n()) %>%
  pull(number_emails)

number_emails_read <- latest_data %>%
  filter(str_detect(email_read, "Yes")) %>%
  summarise(emails_read = n()) %>%
  pull(emails_read)

number_emails_replied <- latest_data %>%
  filter(str_detect(email_reply, "Yes")) %>%
  summarise(emails_replied = n()) %>%
  pull(emails_replied)

mean_view_time <- latest_data$time_to_view %>%
  mean(na.rm = TRUE) %>%
  as.numeric(units = "mins") %>%
  round(2)
```

*Question*: Did you read the contents of the email?

*Question*: Did you/will you reply to this email at any point in the foreseeable future?

*Question*: How long did it take for you to view this email?

These questions were written in order to get insights into what I do when I receive an email. Do I actually read the contents? Will I actually reply? How long did it take me to get around to dealing with the email? Of the `r number_of_emails` emails received, the contents of **`r number_emails_read` emails were read**, and **`r number_emails_replied` emails were replied to**. The average amount of time to view an email was **`r mean_view_time` minutes**.

```{r}
ggplot(data = latest_data) + 
  geom_bar(aes(x = email_read,
               fill = email_reply)) +
  labs(title = "Read Status of Emails",
       x = "Email Read Status",
       y = "Number of Emails")

ggplot(data = latest_data) +
  geom_bar(aes(x = time_to_view)) +
  labs(title = "Time to View each Email",
       x = "Time to View",
       y = " Number of Emails")
```

### Behaviour after an Email is received

```{r}
# summary values for after receiving
num_emails_deleted <- latest_data %>%
  filter(str_detect(deleted, "Yes")) %>%
  summarise(deleted = n()) %>%
  pull(deleted)

min_inbox_size <- latest_data$inbox_size %>%
  min(na.rm = TRUE) %>%
  round(2)

max_inbox_size <- latest_data$inbox_size %>%
  max(na.rm = TRUE) %>%
  round(2)
```

*Question*: Did you delete this email?

*Question*: How many emails do you currently have in your inbox?

These questions were included to determine what happens to emails once I have viewed them. Do I delete them? How many emails do I not delete and leave in the inbox? Of the `r number_of_emails` emails received, **`r num_emails_deleted` emails were deleted** upon receival. The minimum and maximum number of emails in my inbox at any one time were **`r min_inbox_size`** emails and **`r max_inbox_size`** emails respectively.

```{r}
ggplot(data = latest_data) + 
  geom_bar(aes(x = deleted,
               fill = category)) +
  labs(title = "Were Emails Deleted?",
       x = "Deletion Status",
       y = "Number of Emails")
```